Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-05-23 paper/supplementary.tex
supplementary

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm]{figures/pvalues_vertical.pdf}
  \caption{We show the average value and the standard deviation of the coefficients obtained with out method during the trials. the $\star$  symbol corresponds to statistically significant (t-test) nonzero values. We notice in particular that the letters q, x, y are under-represented, as expected. Similarly there were only few proper nouns (PROPN) in text corpora. }
  \label{fig:ridgebaselineresult}
\end{figure}
